Theories of deliberated judgment

### 2022-07-17 simple.tex
A new hope

\begin{document}
\title{A definition of descriptive theories of choice with normative power}
\author{Olivier Cailloux}
\affil{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 PARIS, FRANCE\\
	\href{mailto:olivier.cailloux@dauphine.fr}{olivier.cailloux@dauphine.fr}
}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

@@

\section{Introduction} 
This article defines theories that are prescriptive and empirical.
They are prescriptive in that the claim $a \succ b$ has the semantics of recommending choosing $a$ rather than $b$ when both are available.
They are empirical in that the validity of their recommendations rests on the basis of a mild axiom (compared to usual normative theories such as Savage’s Expected Utility theory) together with empirical claims, thus, claims that observations can falsify.

>>>>

\begin{document}
\title{Theories of deliberated judgment}
\author{Olivier Cailloux}
\affil{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 PARIS, FRANCE\\
	\href{mailto:olivier.cailloux@dauphine.fr}{olivier.cailloux@dauphine.fr}
}
\makeatletter
	\hypersetup{
		pdfsubject={Epistemology},
		pdfkeywords={Decision aiding, Decision making, Argumentation}
	}
\makeatother
\maketitle

@@

\section{Introduction} 
Classical descriptive theories of choice in economics are limited to shallow observations.

This article defines theories that are prescriptive and empirical.
They are prescriptive in that the claim $a \succ b$ has the semantics of recommending choosing $a$ rather than $b$ when both are available.
They are empirical in that the validity of their recommendations rests on the basis of a mild axiom (compared to usual normative theories such as Savage’s Expected Utility theory) together with empirical claims, thus, claims that observations can falsify.
